---
title: "STATS 250 Lab 8 Report"
author: "YOUR NAME GOES HERE IN QUOTES"
date: "TODAY'S DATE GOES HERE IN QUOTES"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
    css: assets/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(checkmate))
  install.packages('checkmate')
source("plot_norm.R")
source("prop_test.R")
```

# Instructions

Welcome to Lab 8! Complete the following exercises designed to help you understand the simulation process for making inference about a population proportion. It is important that you keep your answers inside the ".answer" blocks. Do NOT delete the three colon blocks (:::) and keep your responses between them. Use the tutorial for help, and feel free to ask questions on Piazza or email your lab instructor.

Depending on your instruction method (synchronous or asynchronous), complete the following exercises collaboratively.

1. **Synchronous remote:** Work with your peers in breakout rooms during the synchronous lab.
1. **Asynchronous remote:** Use Piazza for asynchronous collaboration.

**Collaborators:** If applicable, replace this text with the names of anyone you collaborated with on this project.

**NOTE:** If you perform a calculation in R and assign it a name but do not print the value in your knitted document, we reserve the right to deduct points.

# Background

:::{.background}
A 2012 Gallup Poll surveyed Americans about their employment status and whether or not they have diabetes. The survey results indicate that 1.5% of the 47,774 employed (full or part time) and 2.5% of the 5,855 unemployed 18-29 year olds have diabetes. Is there a difference in the rates of employment for the two groups, those who have diabetes and those who do not have diabetes?
:::

# Lab Assignment

## Question 1
:::{.question}
Create a two-way table to present the results of this study. You'll need to define what a success and failure are, as well as what Group A and Group B are. Round to whole numbers of people.
:::

:::{.answer}
- A **Success** is 
- A **Failure** is 
- **Group A** is
- **Group B** is


|             | Group A | Group B | Total |
|:-----------:|:-------:|:-------:|:-----:|
| **Failure** |         |         |       |
| **Success** |         |         |       |
| **Total**   |         |         |       |

:::

## Question 2
:::{.question}
State the appropriate hypotheses to test for a difference in the rates of employment for the two groups, those who have diabetes and those who do not have diabetes.
:::

:::{.answer}
- $H_0$: Replace this text with your null hypothesis
- $H_a$: Replace this text with your alternative hypothesis
:::

## Question 3
:::{.question}
Compute the value of the pooled estimate of the sample proportion. Use R as a calculator to compute this result. Make sure your answer is printed in your knitted document.
:::

:::{.answer}
```{r question3, error = T}
# Replace this comment with code required for Question 3. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 4
:::{.question}
Check the conditions necessary to complete this hypothesis test. Use R as a calculator for your computations, then discuss whether each condition has been met or not. You do not need to discuss independence here; we can assume the independence assumptions have been reasonably met.
:::

:::{.answer}
```{r question4, error = T}
# Replace this comment with code required for Question 4. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

Replace this text with your answer to Try It 4.
:::

## Question 5
:::{.question}
Use `prop_test()` to find the value of the test statistic and the p-value. Report your test statistic and p-value below.
:::

:::{.answer}
```{r question5, error = T}
# Replace this comment with code required for Question 5. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```

- The value of the test statistic is **replace this with the value of the test statistic**.
- The p-value is **replace this with the p-value**.
:::

## Question 6
:::{.question}
Use `plot_norm()` to plot the distribution of the test statistic. *Hint: the test statistic is a Z test statistic, and Z values are on the ... distribution.*.
:::

:::{.answer}
```{r question6, error = T}
# Replace this comment with code required for Question 6. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 7
:::{.question}
Use `pnorm()` to help you find the probability of observing this test statistic or a more extreme value. *Hint: Think about the picture we made in Try It 6 - we will need to find a two-sided probability.* 
:::

:::{.answer}
```{r question7, error = T}
# Replace this comment with code required for Question 7. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 8
:::{.question}
Check the conditions required to compute a confidence interval using the data.
:::

:::{.answer}
```{r question8, error = T}
# Replace this comment with code required for Question 8. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
:::

## Question 9
:::{.question}
Compute a 90% confidence interval for the true difference in rates in employment for the two groups, those with diabetes and those without diabetes. Provide the values below as a percentage.
:::

:::{.answer}
```{r question9, error = T}
# Replace this comment with code required for Question 9. (Remember that this text is a comment, so R ignores it; you can delete it if you want.)

```
The 90% confidence interval for the true difference in rates in employment for the two groups, those with diabetes and those without diabetes, is **______%** to **______%**.

:::

# Wrap-Up and Submission

At the top of the document, make sure you've changed the `author` field to your name (in quotes!). If you'd like, change the date as well.

When you've finished the lab, click the **Knit** button one last time.

## Submission instructions

### If you're using RStudio Cloud

1.  In the Files pane, check the box next to `lab08-report.html`.
2.  Click More \> Export...
3.  Click Download and save the file on your computer in a folder you'll remember and be able to find later. You can just call the file `lab08-report.html` or whatever else you'd like (as long as you remember what you called it).

### If you're using RStudio installed on your computer

1.  locate the `lab08-report.html` file on your computer. The file will be saved in the location indicated at the top of the files pane.

### Submission to Canvas

1.  Click the "Assignments" panel on the left side of the page. Scroll to find "Lab 8", and open the assignment. Click "Submit Assignment".
2.  Towards the bottom of the page, you'll be able to choose `lab08-report.html` from the folder you saved it in from RStudio Cloud or noted if you're using RStudio Desktop. **You will only be able to upload a .html file -- do not upload any other file type.**
3.  Click "Submit Assignment". You're done!
